Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-12 Scripts/Initial_Analysis.Rmd
Created top 5 stocks plot

>>>>

##### Fig. N3 Mapping the time of emergence Of Top stocks

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  # group_by(sau_fishing_entity,fishing_entity_id,tresh,variable) %>% 
  # summarise(sum_value = sum(value,na.rm=T)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 10 most valuable stocks
  top_n(5,value)

# Per EEZs
top_toe <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(eezid,sau_fishing_entity,geo_region,tresh,taxon_key) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(mean_yr = mean(emerging_yr,na.rm=T)) %>% 
  right_join(top_stocks_per_country,
             by = c("sau_fishing_entity","geo_region","tresh","taxon_key")
             ) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  summarise_at(vars(mean_yr),
               c("mean"=mean,
                 "sd" = sd)) %>% 
  mutate(
    geo_region = ifelse(is.na(geo_region),"Other",geo_region)
  )

###### The bar option by UN sub region

# Create data
Species_Data <- top_toe %>% 
  filter(tresh == selected_tresh,
         variable == "value") %>% 
  mutate(mean = mean-2000,
         group = geo_region)

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Species_Data$group)
empty_bar <- 5
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,mean)
Species_Data$id <- seq(1, nrow(Species_Data))

# Species_Data$id <- seq(1, nrow(Species_Data))

# Get the name and the y position of each label
label_data <- Species_Data 
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- Species_Data %>% 
  group_by(group) %>% 
  summarize(start=min(id), 
            end=max(id) - empty_bar, 
            median = median(mean, na.rm = T)
  ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
# grid_data <- grid_data[-1,]
# grid_data[1,2] <- 5 # Manually include bathydemerssal
# grid_data[1,3] <- 1

un_regions <- grid_data %>% 
  select(group)

ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=mean,
           fill=mean)
) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=mean,
               fill=mean),
           stat="identity",
           alpha=0.5
  ) +
  geom_segment(data=grid_data,
               aes(x = end, y = 30, xend = start, yend = 30),
               colour = "grey90", alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_bar(aes(x=as.factor(id),
               y=mean,
               fill=mean
  ),
  stat="identity",
  alpha=0.5) +
  annotate("text", 
           x = 0.5,
           y = 37,
           label = "UN Agenda",
           color= "grey60", 
           size=3, 
           angle=-5
  ) +
  # Country names
  geom_text(data=label_data,
            aes(x=id, 
                y= 100,
                label=sau_fishing_entity,
                hjust=hjust),
            color="black",
            fontface="italic",
            alpha = 1,
            size = 4 ,
            angle = label_data$angle,
            inherit.aes = FALSE) +
  # Continents labels
  # geom_text(data=base_data,
  #           aes(x = title,
  #               y = 85, 
  #               label=group), 
  #           # hjust=c(1,1,1,0,0,0),
  #           colour = "black",
  #           # angle = myAng,
  #           size=5,
  #           fontface="bold",
  #           inherit.aes = FALSE) +
  ylim(-100,100) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14, face = "bold"),
    legend.title.align = 0.5,
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(colour = "white"),
    legend.direction="horizontal",
    legend.key.width = unit(3, 
                            "line")
  ) +
  coord_polar(start = 0) +
  scale_fill_viridis("Average year of range shift\nfor top 5 most valuable stocks",
                     limits = c(0,100),
                     breaks = seq(0,100,20),
                     labels = seq(2000,2100,20),
                     direction = -1
  ) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

ggsave(
  plot = last_plot(),
  width = 13,
  height = 13,
  units = "in",
  filename = "./Figures/top_stocks_circular_trend.png"
)

###### The Map option with tops

```{r the map}

# Create data
Top_map_data <- top_toe %>% 
  filter(tresh == selected_tresh,
         variable == "value") %>% 
  mutate(mean = mean-2000) %>%
  arrange(mean)

# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
# tresh_list <- c("tresh_one","tresh_two")

  # Value Map
  World_map_part <- World_map_nemer %>% 
  filter(
    tresh ==  ,
    variable == "value"
  )

##### New Fig. 4. Top shifting stocks/EEZs weighted (proportion)

```{r, top_stocks_eez, eval = F, echo = F}

Value_map_data %>% 
  group_by(variable,tresh) %>% 
  top_frac(0.10,participation) %>% 
  filter(tresh == "tresh_two",
         variable == "value") %>% 
  # View()
  left_join(Sau_data) %>% 
  group_by(variable,tresh) %>% 
  top_frac(0.10,value) %>%
  left_join(my_path("G","SAU","exploited_species_list.csv",read = T)) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = common_name,
      y = value
    ),
    stat = "identity"
  ) +
  facet_wrap(~sau_fishing_entity,
             scale = "free") +
  theme(axis.text.x = element_text(angle = 90))
